---
title: "QMM_Assign5"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

#Problem 1 [DEA]
===============================================================================
  **Problem Statement:** The Hope Valley Health Care Association owns and operates six nursing homes in adjoining states. An evaluation of their efficiency has been undertaken using two inputs and two outputs. The inputs are staffing labor (measured in average hours per day) and  the cost of supplies (in thousands of dollars per day). The outputs are the number of  patient-days reimbursed by third-party sources and the number of patient-days reimbursed privately.

Formulating the problem as lp to get the weight for  Facility 1

LP formulation:
================================================
// Objective Function
max: 14000 u1 + 3500 u2;

/* Constraints */

14000 u1 + 3500 u2 - 150 v1 - 0.2 v2 <= 0;

14000 u1 + 21000 u2 - 400 v1 - 0.7 v2 <= 0;

42000 u1 + 10500 u2 - 320 v1 - 1.2 v2 <= 0;

28000 u1 + 42000 u2 - 520 v1 - 2.0 v2 <= 0;

19000 u1 + 25000 u2 - 350 v1 - 1.2 v2 <= 0;

14000 u1 + 15000 u2 - 320 v1 - 0.7 v2 <= 0;

150 v1 + 0.2 v2 = 1;

===================================================================
```{r}
library(Benchmarking)
library(lpSolveAPI)
Facility1 <- read.lp("Health.lp")
```

**Questions**
=============
  1) Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH. 
  2) Determine the Peers and Lambdas under each of the above assumptions 
  3) Summarize your results in a tabular format
  4) Compare and contrast the above results 

```{r}
solve(Facility1)
get.objective(Facility1)     #the lp was able to achieve the max efficiency for Facility 1
get.variables(Facility1)    #The proposed inputs and outputs weights for maximum efficiency 
```

First we type our inputs and outputs as vectors. 

We have 2 inputs  (Staff hours, Supplies) and 2 outputs ("Reimbursed Patient_Days","Privately Paid Patient_Day) .
```{r}
x <- matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y) <- c("Reimbursed Patient_Days","Privately Paid Patient_Days")
colnames(x) <- c("Staff_Hours", "Supplies")
print(x)
print(y)
Table<- cbind(x,y)
row.names(Table) =  c("Fac1", "Fac2", "Fac3", "Fac4", "Fac5", "Fac6")
Table
```


Next we run DEA Analysis under all DEA assumptions (FDH, CRS, VRS, IRS, DRS, and FRH)
```{r}
#Constant returns to scale, convexity and free disposability
CRS <- dea(x,y, RTS = "crs") # provide the input and output . The results show that Facilities 1,2,3,4 are efficient whereas facilities 5,6 have efficiency rates of 98% and 87% respectively. 
print(CRS)
peers(CRS)    # identify the peers. The peers units for for facilities 5,6 are 1,2,4 

CRS_Weights <- lambda(CRS)    # identify the relative weights given to the peers. The weights for facility 4 are 0.20, 0.08, 0.54. The weights for facility 6 are 0.34, 0.39, 0.13
#Free disposability hull

FDH <- dea(x,y, RTS= "fdh")
FDH  #all facilities are efficient 
peers(FDH)  #the peer for each facility is itself

FDH_Weights <- lambda(FDH)
#Variable returns to scale, convexity and free disposability
VRS <- dea(x,y, RTS = "vrs")
VRS    #All facilities are efficient except for facility 6
peers(VRS)   #peers for facility 6 are 1,2,5

VRS_Weights <- lambda(VRS)
#Increasing returns to scale, (up-scaling, but not down-scaling), convexity and free disposability
IRS <- dea(x,y, RTS= "irs")
IRS    #All facilities are efficient except for facilit
peers(IRS)    #peers for facility 6 are 1,2,5

IRS_Weights <- lambda(IRS)
#Decreasing returns to scale, convexity, down-scaling and free disposability
DRS <- dea(x,y, RTS= "drs")  #DRS gave same results as CRS
DRS     #All facilities are efficient except for facility 5,6
peers(DRS)  # The peers units for for facilities 5,6 are 1,2,4
DRS_Weights <- lambda(DRS)
  
FRH <- dea(x,y, RTS= "add")
FRH  #all facilities are efficient
peers(FRH)    #the peer unit for each facility is itself
FRH_Weights <- lambda(FRH)
```


```{r}
as.data.frame(Table)
Df <-data.frame (CRS = c(1.0000, 1.0000, 1.0000, 1.0000, 0.9775, 0.8675),
FDH= c(1,1,1,1,1,1), VRS= c(1.0000, 1.0000, 1.0000, 1.0000, 1.0000, 0.8963),IRS =c( 1.0000, 1.0000, 1.0000, 1.0000, 1.0000 ,0.8963), DRS= c(1.0000 ,1.0000 ,1.0000, 1.0000, 0.9775, 0.8675), FRH= c(1,1,1,1,1,1))
Df
#Now we look at the efficiency results at each facility in every DEA assumption. CRS and DRS give same results, FDH and FRH gave same results, and finally both VRS and IRS gave same results as well.
```

```{r}
Results <- cbind(Table,Df)
Results[,-c(1:4)]

#Summary of the weights assigned to each Facility in every DEA assumption

Weights_tbl <- cbind(FDH_Weights, CRS_Weights, VRS_Weights, IRS_Weights, DRS_Weights, FRH_Weights)

row.names(Weights_tbl) =   c("Fac1", "Fac2", "Fac3", "Fac4", "Fac5", "Fac6")

colnames(Weights_tbl) <- c("FDH","FDH", "FDH", "FDH","FDH","FDH", "CRS", "CRS", "CRS", "CRS", "VRS", "VRS", "VRS","VRS", "VRS", "IRS", "IRS", "IRS", "IRS","IRS", "DRS", "DRS", "DRS", "DRS", "FRH", "FRH", "FRH", "FRH", "FRH","FRH") 

as.data.frame(Weights_tbl)   #the table summarizes  the weights for inputs and outputs for  each facility under each DEA assumption.
```

**DEA Analysis Summary**
==============================================
For Hope Vally Health Care Association: Under FDH and FRH all facilities are efficient, under CRS and DRS all facilities were efficient except for Facility 5,6. Under VRS and IRS assumptions all except for facility 6 were efficient.  The peer units for efficient facilities are themselves. Under VRS and IRS assumption the peers unit for inefficient facilities were 1,2 and 5. Under CRS and DRS, the peers unites were 1,2,and 4. 


## *Problem 2* [Goal Programming]
================================================
Emax Corporation Problem:

Maximize Z = P - 6C - 3D, where
  P = total (discounted) profit over the life of the new products,
  
  C = change (in either direction) in the current level of employment,
  
  D = decrease (if any) in next year’s earnings from the current year’s level.

-- P= 20 x1 + 15 x2 + 25 x3;

-- y1= 6 x1 + 4 x2 + 5 x3 - 50;

-- y2= 8 x1 + 7 x2 +5 x3 - 75

y1+ is going over the employment level goal and the weighted penality is 6

y1- is going under the employment level goal and the weighted penality is 6


y2+ is going over the earnings goal for next year- no penality

y2- is going under the earnings goal for next year and the peanlity is 3.


x1 is the quantity of product 1 to be produced

x2 is the quantity of product 2 to be produced

x3 is the quantity of product 3 to be produced 


LP formulation:
================================================
// Objective function
max: 20x1 + 15x2 + 25x3 - 6 y1p - 6 y1m - 3 y2m;

// Constraints

6x1 + 4x2 + 5x3 + y1p - y1m = 50;

8x1 + 7x2 + 5x3 + y2p - y2m = 75;

================================================

```{r}
library(lpSolveAPI)
Emax_GP <- read.lp("Emax.lp")
Emax_GP
```

Solving the problem
```{r}
solve (Emax_GP)
get.objective(Emax_GP)
```

Emax need to produce 15 units of product 3 and none of product 1 and  2 to achieve 225 millions in profit. The employment level will go over the goal by 2500
```{r}
get.variables(Emax_GP)
```





